Geometric models reveal behavioral and neural signatures of transforming naturalistic experiences into episodic memories

### 2020-09-03 paper/main.tex
shrank fig 5
inputted Andy's edits -- "ship it!"

In addition to examining how precisely and distinctively participants recalled individual events, one may also use these metrics to summarize each participant's performance by averaging across a participant's event-wise precision or distinctiveness scores.  This enables us to quantify how precisely a participant tended to recall subtle within-event details, as well as how specific (distinctive) those details were to individual events from the episode.  Participants' average precision and distinctiveness scores were strongly correlated ($r(15) = 0.90, p < 10^{-5}$).  This indicates that participants who tended to precisely recount low-level details of episode events also tended to do so in an event-specific way (e.g., as opposed to detailing recurring themes that were present in most or all episode events; this behavior would have resulted in high precision but low distinctiveness).  We found that, across participants, higher precision scores were positively correlated with both the hand-annotated ($r(15) = 0.60, p = 0.010$) and model-estimated ($r(15) = 0.90, p < 0.001$) numbers of events that participants recalled.  Participants' average distinctiveness scores were also correlated with both the hand-annotated ($r(15) = 0.45, p = 0.068$) and model-estimated ($r(15) = 0.71, p = 0.001$) numbers of recalled events.

>>>>

In addition to examining how precisely and distinctively participants recalled individual events, one may also use these metrics to summarize each participant's performance by averaging across a participant's event-wise precision or distinctiveness scores.  This enables us to quantify how precisely a participant tended to recall subtle within-event details, as well as how specific (distinctive) those details were to individual events from the episode.  Participants' average precision and distinctiveness scores were strongly correlated ($r(15) = 0.90, p < 10^{-5}$).  This indicates that participants who tended to precisely recount low-level details of episode events also tended to do so in an event-specific way (e.g., as opposed to detailing recurring themes that were present in most or all episode events; this behavior would have resulted in high precision but low distinctiveness).  We found that, across participants, higher precision scores were positively correlated with the numbers of both hand-annotated scenes ($r(15) = 0.60, p = 0.010$) and model-estimated events ($r(15) = 0.90, p < 0.001$) that participants recalled.  Participants' average distinctiveness scores were also correlated with both the hand-annotated ($r(15) = 0.45, p = 0.068$) and model-estimated ($r(15) = 0.71, p = 0.001$) numbers of recalled events.
